### 2023-12-28 thesis/chapters/02-analysis-B-features.tex
Fix machinery information and finish Resume

It is important to note that the design of features is not a standalone step in the machine learning pipeline but it should be performed iteratively to improve the target model. Signal features are computed in the time, frequency, and time-frequency domain~\cite{brito_fault_2021}.

@@

In the spectral domain, we can obtain usual statistical properties of the distribution being spectral centroid, skew and kurtosis. Additionaly spectral roll-on and roll-off, fundamental frequency, spectral flux, signal to noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.

@@

\section{Feature transformations} \label{section:feature-selection}
Numerical features from the feature extraction phase have non-normal distributions and span the range of scales. Broad differences among features skew the spread in the particular axis. Inevitably it can degrade the discernment of fault diagnostics models that map input onto smooth function as regression does~\cite{zheng_feature_2018}. The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.

>>>>

It is important to note that the design of features is not a standalone step in the machine learning pipeline but it should be performed iteratively to improve the target model. Signal features are computed in the temporal and spectral domain~\cite{brito_fault_2021}.

@@

In the spectral domain, we can obtain usual statistical properties of the distribution being spectral centroid, skew and kurtosis. Additionaly spectral roll-on and roll-off, fundamental frequency, entropy, negentropy, spectral flux, signal to noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.

@@

\section{Feature transformations} \label{section:feature-selection}
Numerical features from the feature extraction phase have non-normal distributions and span wide ranges. Broad differences among features skew the spread in the particular axis. Inevitably it can degrade the discernment of fault diagnostics models that map input onto smooth function as regression does~\cite{zheng_feature_2018}. The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.

### 2023-12-28 thesis/chapters/02-analysis-C-diagnostics.tex
Write research questions in design section and place illustations
Fix machinery information and finish Resume

The measurements coming in the steaming fashion have to be processed in a single pass. The detection model must deal with the minimal admissible assumptions about the nature of the input events. The outliers are based on non-parametric statistical models, nearest-neighbor clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
\bigbreak

@@

Quality of clustering results is evaluated by \emph{Silhouette score} in the range [-1; 1]. It demands points within clusters to have high cohesion and at the same time to have large separation from other clusters. The low score indicates a too little or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/DenStream.png}
    \caption{DenStream~\cite{amini_density_2012}}
    \label{fig:denstream}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/HS-Tree.png}
    \caption{Half-space tree~\cite{tan_fast_2011}}
\end{figure}

@@

\subsection{Classification}
Accurate multi-class classification of machine fault causes out of the characteristics of known ones is a much more difficult task than novelty detection. Universal enough fault baseline has to be recorded and transformed into feature space. Interactions among fault root causes have to be considered. We are aware of rapid advances in knowledge transfer for deep neural networks~\cite{maurya_condition-based_2021}. So far, solutions seem not production-ready and hard to explain. Therefore, we opt to use a simpler model.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/kNN.png}
        \caption{kNN with k = 5}
        \label{fig:knn}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/M-tree.png}
        \caption{M-tree data structure}
        \label{fig:m-tree}
    \end{subfigure}
    \caption{Nearest neighbors classification algorithm~\cite{chen_skyline_2009}}
\end{figure}

The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, or \emph{Manhatann distance} (Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020}. The optimal $k$ parameter is set in supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate. The demanding neighborhood queries are sped up using spatial index in spatial databases that utilizes search tree such as kd-tree, R-tree, or M-tree.

@@

\subsection{Incremental learning}
Online and incremental machine learning operates in the streaming setting updating the model parameters with each new incoming event or in mini-batches. This approach finds its use in big data processing when the whole dataset is not available in advance or cannot be processed at once because of memory limitations.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{assets/incremental-learning.png}
    \caption{Incremental learning deployment architecture~\cite{gaia_online_2022}}
    \label{fig:online-learn-arch}
\end{figure}

>>>>

The measurements coming in the steaming fashion have to be processed in a single pass. The detection model must deal with the minimal admissible assumptions about the nature of the input events. The outliers are derived based on non-parametric statistical models, nearest-neighbor clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
\bigbreak

@@

Quality of clustering results is evaluated by \emph{Silhouette score} in the range [-1; 1]. It demands for points within clusters to have high cohesion and at the same time to have large separation from other clusters. The low score indicates a too little or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/analysis/DenStream.png}
    \caption{DenStream~\cite{amini_density_2012}}
    \label{fig:denstream}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/analysis/HS-Tree.png}
    \caption{Half-space tree~\cite{tan_fast_2011}}
\end{figure}

@@

\subsection{Classification}
Accurate multi-class classification of machine fault causes according to the characteristics of known ones is a much more difficult task than novelty detection. Fault combinations have to be recorded and transformed into feature space. Interactions among fault root causes have to be considered. We are aware of rapid advances in knowledge transfer for deep neural networks~\cite{maurya_condition-based_2021}. So far, solutions seem not production-ready and hard to explain. Therefore, we opt to use a simpler model.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/analysis/kNN.png}
        \caption{kNN with k = 5}
        \label{fig:knn}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/analysis/M-tree.png}
        \caption{M-tree data structure}
        \label{fig:m-tree}
    \end{subfigure}
    \caption{Nearest neighbors classification algorithm~\cite{chen_skyline_2009}}
\end{figure}

The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc. (Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}. The optimal $k$ parameter is set in supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate. The demanding neighborhood queries are sped up using spatial index in spatial databases that utilizes search tree such as kd-tree, R-tree, or M-tree.

@@

\subsection{Incremental learning}
Online or incremental machine learning operates on the streaming data updating the model parameters with each new incoming event or in mini-batches. This approach finds its use in big data processing when the whole dataset is not available in advance or cannot be processed at once because of memory limitations.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{assets/analysis/incremental-learning.png}
    \caption{Incremental learning deployment architecture~\cite{gaia_online_2022}}
    \label{fig:online-learn-arch}
\end{figure}

### 2023-12-28 thesis/chapters/03-design.tex
Fix machinery information and finish Resume

\section{Research questions}
This thesis aims to provide answers to four research questions formulated in broader sense. The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines. The \textbf{research questions} are:
\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
    \itemsep0pt
	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
	\item What is the reduction in transmission goodput when chosen signal features are used?
	\item What accuracies of prediction models can be achieved with various feature subsets?
	\item How can machinery faults be continuously identified and predicted based upon collected events?
\end{enumerate}

@@

\section{Dataset exploration}
In establishing the validity of methods to be deployed on the sensor node we explore the MaFaulDa dataset. It is the largest known machinery fault collection, so it is possible to create multiple subsets based on requested conditions.

@@

The Euclidian norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure \ref{fig:design:feature-range}.

@@

\subsection{Feature selection}
The objective of feature selection is to find a subset of the most relevant predictors in each domain. As a starting point, the set consists of 3 non-correlated attributes under diverse conditions. Ultimately a number of chosen features is to be tweaked to increase prediction accuracy. Four criteria are combined to put together 24 scenarios that filter rows from MaFaulDa:
\begin{itemize}
\itemsep0pt
\item \textbf{online}: boolean selector that influences whether metrics are calculated in batch or incremental fashion,
\item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
\item \textbf{target variable}: selects column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
\item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
\end{itemize}

@@

\section{K-nearest neighbor classifier}
We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets. kNN classifier being a lazy learner means it can be adapted easily from offline to online context. Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values. Voronoi diagrams can display these regions and explain the model in that way. Batch learning in kNN serves here as a target performance whose attainment is desirable with online learning.

\subsection{Batch models}
Three types of kNN model experiments run with hold-out validation in batch setting. 
First, the model learns all extracted features, so no feature selection occurs. Then, the brute-force method searches for a combination of three features with the highest training accuracy. In the end, the model performance for three attributes chosen by feature selection techniques is compared to principal components.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-temporal-confusion-matrix-fault.png}
        \caption{Prediction for 6 fault classes in testing set with temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-spectral-confusion-matrix-fault.png}
        \caption{Prediction for 6 fault classes in testing set with spectral domain features}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-temporal-confusion-matrix-anomaly90.png}
        \caption{Prediction of high severity anomalies in testing set with temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-spectral-confusion-matrix-anomaly90.png}
        \caption{Prediction of high severity anomalies in testing set with spectral domain features}
    \end{subfigure}
    \caption{Confusion matrix of kNN predictions on bearing position A}
    \label{fig:design:knn-confusion-matrix}
\end{figure}

@@

Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}. In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree. The most inaccuracies in the temporal domain are between misalignment and bearing race faults. In the spectral domain, the model confuses imbalance and bearing faults because mass to unbalance is hung onto the shaft to cause bearing defects.

@@

\caption{kNN model performance trained on all extracted features}

@@

Next, we exhaustively list all combinations of three features and look at the range of model performances generated. There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate kNN models for temporal domain features and 165 for the spectral domain. The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques. Accuracies of kNN algorithm for different target variables are in Figure \ref{fig:design:feature-combinations-knn}.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-3-features-combinations-train.png}
        \caption{Testing set}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-3-features-combinations-test.png}
        \caption{Training set}
    \end{subfigure}
    \caption{Range of prediction accuracy in all kNN models with subset of 3 features. Subplots show three different predicted variables.}
    \label{fig:design:feature-combinations-knn}
\end{figure}

Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-knn}. Worst accuracies occur for temporal features in multiclass classification 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features. An improvement would come with increasing the number of features, using a different base feature set with greater discriminatory power, or using a more sophisticated model.

\begin{table}[ht!]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{|r|r|r|l|r|r|}
\hline
\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Training \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Testing \\ accuracy\end{tabular}} \\ \hline
\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, skewness, shape\}         & 0.9559                & 0.9328               \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, noisiness, entropy\} & 0.9818                & 0.9707               \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, shape\}         & 0.9106                & 0.8591 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, kurtosis, entropy\}  & 0.9750                & 0.9505               \\ \hline
\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{std, kurtosis, pp\}            & 0.9085                & 0.8551               \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, std, roll-on\}      & 0.9495                & 0.9185               \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, kurtosis\}      & 0.8369                & 0.7654 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, std, roll-off\}     & 0.9067                & 0.8584               \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Features with the highest accuracies on the training set found combinatorically}
\label{tab:design:feature-combinations-knn}
\end{table}

The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-knn}. Their prediction accuracies in kNN models are subpar to optimal sets. However, the advantage is that the feature election process is not so computationally taxing. On bearing A, validation set accuracies for fault diagnostics are 85\% and 92\%, for each of the domains. Because of the low k hyperparameter value, models are overtrained either way.

\begin{table}[ht!]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{|r|r|r|l|r|r|}
\hline
\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Train \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Test \\ accuracy\end{tabular}} \\ \hline
\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{shape, std, rms\}               & 0.9333                                       & 0.8916                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, flux, entropy\}       & 0.9654                                       & 0.9474                                      \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{std, shape, max\}               & 0.9048                                       & 0.8544                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{roll-off, centroid, skewness\} & 0.9504                                       & 0.9210                                      \\ \hline
\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, shape, crest\}             & 0.8961                                       & 0.8505                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{std, noisiness, entropy\}       & 0.9265                                       & 0.8843                                      \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{pp, crest, skewness\}           & 0.8194                                       & 0.7380                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, roll-on, roll-off\} & 0.8914                                       & 0.8390                                      \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated kNN accuracies.}
\label{tab:design:best-3-features-knn}
\end{table}

@@

Model performance of kNN algorithm preceeded by variety of feature selection methods is compared in Figure \ref{fig:design:knn-accuracy-batch}. Best combination of three features achieves always better than when the model is trained on all features. This has to do with curse of dimensionality phenomenon.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-train.png}
        \caption{Testing set}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-test.png}
        \caption{Training set}
    \end{subfigure} 
    \caption{Batch kNN algorithm prediction accuracy with various feature sets.}
    \label{fig:design:knn-accuracy-batch}
\end{figure}

@@

The kNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in batch context. In this manner, we can compare the training accuracies in the last sample for both models. kNN is set to 5 nearest neighbors and proximity metric of Euclidian distance. Online learning metrics are evaluated in progressive valuation on a dataset that is left unbalanced.

>>>>

\section{Research questions}
This thesis aims to provide answers to four research questions. The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines. The \textbf{research questions} are:
\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
    \itemsep0pt
	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
	\item What is the reduction in transmission goodput when chosen signal features are used?
	\item What accuracies of prediction models can be achieved with various feature subsets?
	\item How can machinery faults be continuously identified and predicted based upon collected events?
\end{enumerate}

@@

\section{Dataset exploration}
In establishing the viability of methods to be deployed in the sensor node, we explore the MaFaulDa dataset. It is the largest known machinery fault collection, so it is possible to create multiple subsets based on requested conditions.

@@

The Euclidean norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure~\ref{fig:design:feature-range}.

@@

\subsection{Feature selection}
The objective of feature selection is to find a subset of the most relevant predictors in each domain. As a starting point, the set consists of 3 non-correlated attributes under diverse conditions. Ultimately a number of chosen features is to be tweaked to increase prediction accuracy. Four criteria are combined to put together 24 scenarios that filter rows from MaFaulDa:
\begin{itemize}
\itemsep0pt
\item \textbf{online}: boolean selector that influences whether metrics are calculated in batch or incremental fashion,
\item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
\item \textbf{predicted variable}: selects column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
\item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
\end{itemize}

@@

\section{K-nearest neighbor classifier}
We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets. kNN classifier being a lazy learner means it can be adapted easily from offline to online context. Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values. Voronoi diagrams can display these regions and explain the model in that way. Batch learning in KNN serves here as a target performance whose attainment is desirable with online learning.

\subsection{Batch models}
Three types of KNN model experiments run with hold-out validation in batch setting. 
First, the model learns all extracted features, so no feature selection occurs. Then, the brute-force method searches for a combination of three features with the highest training accuracy. In the end, the model performance for three attributes chosen by feature selection techniques is compared to principal components.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-fault.png}
        \caption{Prediction for 6 fault classes in testing set with temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-fault.png}
        \caption{Prediction for 6 fault classes in testing set with spectral domain features}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-anomaly90.png}
        \caption{Prediction of high severity anomalies in testing set with temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-anomaly90.png}
        \caption{Prediction of high severity anomalies in testing set with spectral domain features}
    \end{subfigure}
    \caption{Confusion matrix of KNN predictions on bearing position A}
    \label{fig:design:KNN-confusion-matrix}
\end{figure}

@@

Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:KNN-confusion-matrix}. In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree. The most inaccuracies in the temporal domain are between misalignment and bearing race faults. In the spectral domain, the model confuses imbalance and bearing faults because mass to unbalance is hung onto the shaft to cause bearing defects.

@@

\caption{KNN model performance trained on all extracted features}

@@

Next, we exhaustively list all combinations of three features and look at the range of model performances generated. There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate KNN models for temporal domain features and 165 for the spectral domain. The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques. Accuracies of KNN algorithm for different target variables are in Figure \ref{fig:design:feature-combinations-KNN}.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-train.png}
        \caption{Testing set}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-test.png}
        \caption{Training set}
    \end{subfigure}
    \caption{Range of prediction accuracy in all KNN models with subset of 3 features. Subplots show three different predicted variables.}
    \label{fig:design:feature-combinations-KNN}
\end{figure}

Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-KNN}. Worst accuracies occur for temporal features in multiclass classification 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features. An improvement would come with increasing the number of features, using a different base feature set with greater discriminatory power, or using a more sophisticated model.

\begin{table}[ht!]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{|r|r|r|l|r|r|}
\hline
\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Training \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Testing \\ accuracy\end{tabular}} \\ \hline
\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, skewness, shape\}         & 0.9559                & 0.9328               \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, noisiness, entropy\} & 0.9818                & 0.9707               \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, shape\}         & 0.9106                & 0.8591 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, kurtosis, entropy\}  & 0.9750                & 0.9505               \\ \hline
\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{std, kurtosis, pp\}            & 0.9085                & 0.8551               \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, std, roll-on\}      & 0.9495                & 0.9185               \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, kurtosis\}      & 0.8369                & 0.7654 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, std, roll-off\}     & 0.9067                & 0.8584               \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Features with the highest accuracies on the training set found combinatorically}
\label{tab:design:feature-combinations-KNN}
\end{table}

The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-KNN}. Their prediction accuracies in KNN models are subpar to optimal sets. However, the advantage is that the feature election process is not so computationally taxing. On bearing A, validation set accuracies for fault diagnostics are 85\% and 92\%, for each of the domains. Because of the low k hyperparameter value, models are overtrained either way.

\begin{table}[ht!]
\centering
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{|r|r|r|l|r|r|}
\hline
\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Train \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Test \\ accuracy\end{tabular}} \\ \hline
\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{shape, std, rms\}               & 0.9333                                       & 0.8916                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, flux, entropy\}       & 0.9654                                       & 0.9474                                      \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{std, shape, max\}               & 0.9048                                       & 0.8544                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{roll-off, centroid, skewness\} & 0.9504                                       & 0.9210                                      \\ \hline
\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, shape, crest\}             & 0.8961                                       & 0.8505                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{std, noisiness, entropy\}       & 0.9265                                       & 0.8843                                      \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{pp, crest, skewness\}           & 0.8194                                       & 0.7380                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, roll-on, roll-off\} & 0.8914                                       & 0.8390                                      \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated KNN accuracies.}
\label{tab:design:best-3-features-KNN}
\end{table}

@@

Model performance of KNN algorithm preceeded by variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}. Best combination of three features achieves always better than when the model is trained on all features. This has to do with curse of dimensionality phenomenon.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
        \caption{Testing set}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
        \caption{Training set}
    \end{subfigure} 
    \caption{Batch KNN algorithm prediction accuracy with various feature sets.}
    \label{fig:design:KNN-accuracy-batch}
\end{figure}

@@

The KNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in batch context. In this manner, we can compare the training accuracies in the last sample for both models. KNN is set to 5 nearest neighbors and proximity metric of Euclidian distance. Online learning metrics are evaluated in progressive valuation on a dataset that is left unbalanced.
